### 2025-02-27 basic-statistics.qmd
20250227 - clean up

# combine polygons. 
poly1$id <- 3 # alpha, give it the highest number to make it the top layer
poly2$id <- 2 # beta
poly3$id <- 1 # power; 1 - beta
poly <- rbind(poly1, poly2, poly3)
poly$id <- factor(poly$id,  labels=c("power","beta","alpha"))

# plot with ggplot2
ggplot(poly, aes(x,y, fill=id, group=id)) +
  geom_polygon(show.legend=F, alpha=I(8/10)) +
  # add line for treatment group
  geom_line(data=df1, aes(x,y, color="H0", group=NULL, fill=NULL), linewidth=1.5, show_guide=F) + 
  # add line for treatment group. These lines could be combined into one dataframe.
  geom_line(data=df2, aes(color="HA", group=NULL, fill=NULL),linewidth=1.5, show_guide=F) +
  # add vlines for z_crit
  geom_vline(xintercept = z_crit, linewidth=1, linetype="dashed") +
  # change colors 
  scale_color_manual("Group", 
                     values= c("HA" = "#981e0b","H0" = "black")) +
  scale_fill_manual("test", values= c("alpha" = "#0d6374","beta" = "#be805e","power"="#7cecee")) +
  # beta arrow
  annotate("segment", x=0.1, y=0.045, xend=1.3, yend=0.01, arrow = arrow(length = unit(0.3, "cm")), linewidth=1) +
  annotate("text", label="beta", x=0, y=0.05, parse=T, size=8) +
  # alpha arrow
  annotate("segment", x=4, y=0.043, xend=3.4, yend=0.01, arrow = arrow(length = unit(0.3, "cm")), linewidth=1) +
  annotate("text", label="frac(alpha,2)", x=4.2, y=0.05, parse=T, size=8) +
  # power arrow
  annotate("segment", x=6, y=0.2, xend=4.5, yend=0.15, arrow = arrow(length = unit(0.3, "cm")), linewidth=1) +
  annotate("text", label=expression(paste(1-beta, "  (\"power\")")), x=6.1, y=0.21, parse=T, size=8) +
  # H_0 title
  annotate("text", label="H[0]", x=m1, y=0.28, parse=T, size=8) +
  # H_a title
  annotate("text", label="H[1]", x=m2, y=0.28, parse=T, size=8) +
  ggtitle("Statistical Power") +
  # remove some elements
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    panel.background = element_blank(),
    plot.background = element_rect(fill="white"),
    panel.border = element_blank(),
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(size=22))
```

>>>>

# combine polygons
poly1$id <- 3 # alpha, give it the highest number to make it the top layer
poly2$id <- 2 # beta
poly3$id <- 1 # power; 1 - beta
poly <- rbind(poly1, poly2, poly3)
poly$id <- factor(poly$id,  labels = c("power", "beta", "alpha"))

# plot with ggplot2
ggplot(poly, aes(x,y, fill=id, group=id)) +
  geom_polygon(show.legend=F, alpha=I(8/10)) +
  # add line for treatment group
  geom_line(data=df1, aes(x, y, color = "H0", group = NULL, fill = NULL), linewidth = 1.5, show_guide = FALSE) + 
  # add line for treatment group. These lines could be combined into one dataframe.
  geom_line(data=df2, aes(color = "HA", group = NULL, fill = NULL), linewidth = 1.5, show_guide = FALSE) +
  # add vlines for z_crit
  geom_vline(xintercept = z_crit, linewidth=1, linetype="dashed") +
  # change colors
  scale_color_manual(
    "Group",
    values = c("HA" = "#981e0b", "H0" = "black")) +
  scale_fill_manual("test", values= c("alpha" = "#0d6374", "beta" = "#be805e", "power"="#7cecee")) +
  # beta arrow
  annotate("segment", x = 0.1, y = 0.045, xend = 1.3, yend = 0.01, arrow = arrow(length = unit(0.3, "cm")), linewidth = 1) +
  annotate("text", label="beta", x=0, y=0.05, parse=T, size=8) +
  # alpha arrow
  annotate("segment", x = 4, y = 0.043, xend = 3.4, yend = 0.01, arrow = arrow(length = unit(0.3, "cm")), linewidth = 1) +
  annotate("text", label="frac(alpha,2)", x=4.2, y=0.05, parse=T, size=8) +
  # power arrow
  annotate("segment", x = 6, y = 0.2, xend = 4.5, yend = 0.15, arrow = arrow(length = unit(0.3, "cm")), linewidth = 1) +
  annotate("text", label = expression(paste(1-beta, "  (\"power\")")), x = 6.1, y = 0.21, parse = TRUE, size = 8) +
  # H_0 title
  annotate("text", label = "H[0]", x = m1, y = 0.28, parse = TRUE, size = 8) +
  # H_a title
  annotate("text", label = "H[1]", x = m2, y = 0.28, parse = TRUE, size = 8) +
  ggtitle("Statistical Power") +
  # remove some elements
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    panel.background = element_blank(),
    plot.background = element_rect(fill="white"),
    panel.border = element_blank(),
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(size=22))
```

### 2025-02-27 data-visualization.qmd
20250227 - clean up

ggplot2::ggplot(
  data = epa_combined,
  aes(
    x = off_epa,
    y = def_epa)) +
  nflplotR::geom_mean_lines(
    aes(
      x0 = off_epa ,
      y0 = def_epa)) +
  nflplotR::geom_nfl_logos(
    aes(
      team_abbr = team),
      width = 0.065,
      alpha = 0.7) +
  labs(
    x = "Offense EPA/play",
    y = "Defense EPA/play",
    title = "2024 NFL Offensive and Defensive EPA per Play"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) + # horizontal y-axis title
  scale_y_reverse()
```

>>>>

ggplot2::ggplot(
  data = epa_combined,
  aes(
    x = off_epa,
    y = def_epa)) +
  nflplotR::geom_mean_lines(
    aes(
      x0 = off_epa,
      y0 = def_epa)) +
  nflplotR::geom_nfl_logos(
    aes(
      team_abbr = team),
      width = 0.065,
      alpha = 0.7) +
  labs(
    x = "Offense EPA/play",
    y = "Defense EPA/play",
    title = "2024 NFL Offensive and Defensive EPA per Play"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) + # horizontal y-axis title
  scale_y_reverse()
```
